---
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
header-includes:
- \usepackage{xcolor}
- \usepackage{graphicx}
- \usepackage{tcolorbox} % For creating text boxes
- \usepackage{xcolor} % Use color package for customization
- \definecolor{whodarkblue}{RGB}{0, 32, 92}
- \definecolor{wholightblue}{RGB}{0, 154, 222}
- \definecolor{wholightblueshade}{RGB}{121, 181, 227}
- \definecolor{wholightblueshadev2}{RGB}{201, 221, 243}
- \setmainfont{Arial}
- \usepackage{fancyhdr} % Allows customization of headers and footers
- \pagestyle{fancy} % Enable fancy header/footer style
- \fancyhf{}
- "\\fancyhead[L]{\\color{whodarkblue} Health data overview   |   Afghanistan} % Add
  left-aligned content (e.g., section title)"
- \fancyhead[C]{} % Empty center
- "\\fancyhead[R]{\\color{whodarkblue}\\thepage} % Add right-aligned content (e.g.,
  author name)"
- \renewcommand{\headrule}{{\color{whodarkblue}\hrule width\headwidth height\headrulewidth}}
- \renewcommand{\headrulewidth}{0.6pt} % Add a horizontal line with thickness of 0.4pt
- \setlength{\headheight}{30pt} % Increase header height if needed
geometry: margin=1.75cm
---

\thispagestyle{empty}
\pagecolor{whodarkblue}

\begin{flushleft}
{\color{white}\rule{\linewidth}{0.25mm}} \\
\vspace{1.5cm}
{\fontsize{50}{60}\selectfont \color{white} Health Data Overview} \\
\vspace{1.5cm}
{\fontsize{25}{30}\selectfont \color{wholightblueshade} `r toupper("Afghanistan")`}

\vspace*{15cm} 

\end{flushleft}

\begin{flushright}
\includegraphics[width=5cm]{WHO-EN-W-H.png}
\end{flushright}


\newpage
\pagecolor{white}

```{r settings, echo= FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r parameters, echo = FALSE, message = FALSE, include = FALSE, eval = TRUE}
# list2env(params, .GlobalEnv)
```

```{r packages, include=FALSE}
library(tidyverse)
library(treemap)
library(ghost)
# library(sf)
# library(RColorBrewer)
# library(kableExtra)
library(ggpol)
library(extrafont)
library(showtext)
library(patchwork)
library(cowplot)
library(ggnewscale)
library(flextable)
library(whoville)
# library(DemoDecomp)
library(ggrepel)
library(ggbump)
# library(forcats)
library(ggpubr)
library(ggh4x)
library(httr)
library(jsonlite)

load("data_req.rda")
sdg_ <- sdg %>% distinct(IND_UUID, IND_CODE, IND_PER_CODE, IndicatorName, IND_ID) 
```

```{r text_values, include=FALSE}

# total population
total_pop2023 <- pop %>% filter(country == "Afghanistan" & year==2023) %>% pull(totalpop_jul)
total_pop2050 <- pop %>% filter(country == "Afghanistan" & year==2050) %>% pull(totalpop_jul)
total_pop_increase <- round(((as.numeric(total_pop2050) - as.numeric(total_pop2023)) / as.numeric(total_pop2023))*100, digits = 0)

# life expectany
le_2000 <- lehale %>% filter(IndicatorCode=="WHOSIS_000001" & sex=="Both sexes" & year==2000 & country == "Afghanistan") %>% pull(NumericValue)
le_2000_lwr <- lehale %>% filter(IndicatorCode=="WHOSIS_000001" & sex=="Both sexes" & year==2000 & country == "Afghanistan") %>% pull(Low)
le_2000_upr <- lehale %>% filter(IndicatorCode=="WHOSIS_000001" & sex=="Both sexes" & year==2000 & country == "Afghanistan") %>% pull(High)

le_2021 <- lehale %>% filter(IndicatorCode=="WHOSIS_000001" & sex=="Both sexes" & year==2021 & country == "Afghanistan") %>% pull(NumericValue)
le_2021_lwr <- lehale %>% filter(IndicatorCode=="WHOSIS_000001" & sex=="Both sexes" & year==2021 & country == "Afghanistan") %>% pull(Low)
le_2021_upr <- lehale %>% filter(IndicatorCode=="WHOSIS_000001" & sex=="Both sexes" & year==2021 & country == "Afghanistan") %>% pull(High)

change <- abs(le_2021 - le_2000)
change_text <- case_when(
 le_2021 < le_2000 ~ "decreased by",
 le_2000 < le_2021 ~ "improved by"
)

```

```{r pop_pyramid, include=F, message=FALSE}
pop_data <- pop_age %>% 
  filter(country =="Afghanistan" & year %in% c(2023,2050)) %>% 
  mutate(ageg = factor(ageg, 
                       levels = c("0-4", "5-9", "10-14", "15-19", "20-24", "25-29", "30-34", "35-39",
                                  "40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74", "75-79", "80-84", "85+")
                       ))

max_lim <- max(pop_data$total_pop)
pop_data$total_pop <- ifelse(pop_data$sex == "Female", pop_data$total_pop*-1, pop_data$total_pop)

png("pop_pyramid.png", height = 790, width = 700)

# make plot
ggplot() + 
  geom_col(data = pop_data %>% filter(year==2050),
           aes(x= ageg, y = total_pop, fill = sex), width = 0.7, alpha = 0.3, show.legend = F)+
  geom_col(data = pop_data %>% filter(year==2023),
           aes(x= ageg, y = total_pop, fill = sex), width = 0.4, show.legend = F) +

  facet_wrap(~sex, scales = 'free_x', strip.position = "bottom") +
  coord_flip(clip = 'off') +
  scale_fill_manual(values = c("Male" = "#F4A81D",
                               "Female" = "#5B2C86"))+
  facetted_pos_scales(
    y = list(scale_y_continuous(limits = c(-max_lim, 0), expand = c(0,0),
                                ),
             scale_y_continuous(limits = c(0, max_lim), expand = c(0,0),
                                )
             )
    ) +
  theme_classic() +
  theme(
      strip.background = element_blank(),
      strip.text = element_text(family="calibri", size = 20),
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.ticks.y = element_line(color = "white"),
      axis.line.x = element_blank(),
      axis.line.y = element_blank(),
      axis.title.y = element_blank(),
      panel.grid.major.y = element_line(color = "grey"),
      axis.text.y = element_text(family="calibri", size = 20, color = "black")
    )  

dev.off()
```

\begin{minipage}{0.43\textwidth}
\begin{tcolorbox}[colback=wholightblueshadev2, colframe=wholightblueshadev2, title=Overview, coltitle=whodarkblue, fonttitle=\Large\bfseries, height=9cm, boxsep=3mm]

In Afghanistan, the current population is `r total_pop2023` as of 2023 with a projected increase of `r total_pop_increase`\% to `r total_pop2050` by 2050.
\\
\\
Life expectancy at birth (years) has `r change_text` `r round(change,1)` years from `r round(le_2000,1)` [`r round(le_2000_lwr,1)` - `r round(le_2000_upr,1)`] years in 2000 to `r round(le_2021,1)` [`r round(le_2021_lwr,1)` - `r round(le_2021_upr,1)`] years in 2021.

\end{tcolorbox}
\end{minipage}
\hfill
\begin{minipage}{0.5\textwidth}
\large Demographic change 2023 - 2050
\includegraphics{pop_pyramid.png}
\end{minipage}

\
\

\rule{\textwidth}{0.6pt}\color{whodarkblue}
\large Life expectancy and healthy life expectancy by sex, 2000–2021

```{r life_exp_bysex, fig.height=4.3, fig.align='center', fig.width=8}
exp <- lehale %>% 
  filter(IndicatorCode=="WHOSIS_000002" | IndicatorCode=="WHOSIS_000001") %>%
  filter(country=="Afghanistan") %>% 
  mutate(name = ifelse(IndicatorCode=="WHOSIS_000001", "Life expectancy at birth", "Healthly life expectancy at birth")) %>% 
  select(country, year, sex, name, value = NumericValue) %>% 
  mutate(value = round(value, 1)) %>% 
  mutate(name = factor(name, levels = c("Life expectancy at birth", "Healthly life expectancy at birth")))

max <- exp %>% select(value) %>% arrange(desc(value)) %>% filter(row_number()==1) %>% pull()
min <- exp %>% select(value) %>% arrange(value) %>% filter(row_number()==1) %>% pull()

ggplot()+
  geom_line(data = exp, aes(x=year, y=value, color=sex), size = 1) +
  geom_text(data = exp %>% filter(year==2021),
            mapping = aes(x = 2021.5, y = value, label = value, color = sex), show.legend = F, hjust = 0
    # mapping = aes(x = 2021.5, y = value, label = paste0(value, " (", sex, ")"), color = sex), show.legend = F, hjust = 0
    ) +
  facet_wrap(~name, scales = 'free_x', strip.position = "top") +
  scale_y_continuous(limits = c(round(min, 0)-2,round(max, 0)+2)) +
  scale_x_continuous(limits = c(2000, 2024)) +
  scale_color_manual(values = c("Male" = "#F4A81D",
                               "Female" = "#5B2C86",
                               "Both sexes" = "#009ADE")) +
  theme_classic()+
  theme(axis.text=element_text(size=9),
        axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.border = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        axis.line.y = element_blank(),
        axis.line.x = element_line(color = "darkgrey",linetype = 3),
        panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "white"),
        strip.background = element_blank(),
        strip.text = element_text(size = 10)
)
  
```

\newpage

Top causes of death, 2021
\
\normalsize Deaths per 100,000 population
\vspace{-0.5cm} 
```{r cod2021, fig.height=5, fig.align='center', fig.width=9}

cod <- cod21 %>% 
  filter(country=="Afghanistan" & FLAG_TREEMAP==1 & DIM_AGEGROUP_CODE=="TOTAL") %>% 
  group_by(country, sex) %>%
  arrange(region, sex, desc(VAL_DEATHS_RATE100K_NUMERIC)) %>%
  slice(1:10)

names <- cod %>% 
  filter(sex=="Female") %>% 
  arrange(VAL_DEATHS_RATE100K_NUMERIC) %>% 
  pull(DIM_GHECAUSE_TITLE)
color_gradient <- colorRampPalette(c("#d0dde3", "#00205C"))(10)
names(color_gradient) <- names

codf <- cod %>% 
  filter(sex=="Female") %>% 
  ggplot(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = VAL_DEATHS_RATE100K_NUMERIC, fill = DIM_GHECAUSE_TITLE))+
  geom_text(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = -10, label = round(VAL_DEATHS_RATE100K_NUMERIC, 1)), size = 2.5) +
  geom_bar(stat = "identity", show.legend = F, width = 0.8) +
  coord_flip() +
  scale_fill_manual(values = color_gradient) +
  labs(title = "Female") +
  theme_classic()+
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 8, hjust = 0, color = "black")
  )

names <- cod %>% 
  filter(sex=="Male") %>% 
  arrange(VAL_DEATHS_RATE100K_NUMERIC) %>% 
  pull(DIM_GHECAUSE_TITLE)
color_gradient <- colorRampPalette(c("#d0dde3", "#00205C"))(10)
names(color_gradient) <- names

codm <- cod %>% 
  filter(sex=="Male") %>% 
  ggplot(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = VAL_DEATHS_RATE100K_NUMERIC, fill = DIM_GHECAUSE_TITLE))+
  geom_text(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = -10, label = round(VAL_DEATHS_RATE100K_NUMERIC, 1)), size = 2.5) +
  geom_bar(stat = "identity", show.legend = F, width = 0.8) +
  coord_flip() +
  scale_fill_manual(values = color_gradient) +
  labs(title = "Male") +
  theme_classic()+
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 8, hjust = 0, color = "black")
  )

patchwork::wrap_plots(codf, codm, ncol = 2)


names <- cod %>% 
  filter(sex=="Both sexes") %>% 
  arrange(VAL_DEATHS_RATE100K_NUMERIC) %>% 
  pull(DIM_GHECAUSE_TITLE)
color_gradient <- colorRampPalette(c("#d0dde3", "#00205C"))(10)
names(color_gradient) <- names

codb <- cod %>% 
  filter(sex=="Both sexes") %>% 
  ggplot(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = VAL_DEATHS_RATE100K_NUMERIC, fill = DIM_GHECAUSE_TITLE))+
  geom_text(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = -10, label = round(VAL_DEATHS_RATE100K_NUMERIC, 1)), size = 2.5) +
  geom_bar(stat = "identity", show.legend = F, width = 0.8) +
  coord_flip() +
  scale_fill_manual(values = color_gradient) +
  labs(title = "Both sexes") +
  theme_classic()+
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 8, hjust = 0, color = "black")
  )
```

```{r cod2021_, fig.height=5, fig.align='center', fig.width=9}

cod_ <- cod21 %>% 
  filter(country=="Afghanistan" & FLAG_LEVEL==1 & DIM_AGEGROUP_CODE=="TOTAL" & sex =="Both sexes") 
  
names <- cod_ %>% 
  arrange(VAL_DEATHS_RATE100K_NUMERIC) %>% 
  pull(DIM_GHECAUSE_TITLE)
color_gradient <- colorRampPalette(c("#d0dde3", "#00205C"))(4)
names(color_gradient) <- names

codgroup <- cod_ %>% 
  ggplot(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = VAL_DEATHS_RATE100K_NUMERIC, fill = DIM_GHECAUSE_TITLE))+
  geom_text(aes(x=reorder(str_wrap(DIM_GHECAUSE_TITLE, 20), VAL_DEATHS_RATE100K_NUMERIC), y = -30, label = round(VAL_DEATHS_RATE100K_NUMERIC, 1)), size = 2.5) +
  geom_bar(stat = "identity", show.legend = F, width = 0.8) +
  coord_flip() +
  scale_fill_manual(values = color_gradient) +
  labs(title = "By broad cause, both sexes") +
  theme_classic()+
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 8, hjust = 0, color = "black")
  )

patchwork::wrap_plots(codb, codgroup, ncol = 2)
```

\newpage

\Large Health Statistics: Health Status
\
\normalsize Indicator Progress
\vspace{-0.5cm} 
```{r health status, fig.height=10.3, fig.width = 8, fig.align='center', message=F, warning=F}
# ind <- c(
#   "New HIV infections (per 1000 uninfected population)",
#   "Incidence of tuberculosis (per 100 000 population per year)",
#   "Maternal mortality ratio (per 100 000 live births)",
#   "Under-five mortality rate (probability of dying by age 5 per 1000 live births)",
#   "Ambient and household air pollution attributable death rate (per 100 000 population, age-standardized)",
#   "Estimated malaria incidence (per 1000 population at risk)"
#   )

# codes <- c("SDGHIV",
#            "MDG_0000000020",
#            "MDG_0000000026",
#            "MDG_0000000007",
#            "SDGAIRBODA",
#            "MALARIA_EST_INCIDENCE")

getind <- function(){
  ind <- GET(url = "https://ghoapi.azureedge.net/api/Indicator")
  ind2 = fromJSON(rawToChar(ind$content))
  ind3 <- ind2[2]$value
  return(ind3)
}
ind_func <- getind()

response <- GET("https://xmart-api-public.who.int/DATA_/RELAY_MAY2023?$filter=DIM_GEO_CODE_M49%20eq%20'004'")
resultTxt <- content(response, "text")
resultJson <- fromJSON(resultTxt, flatten = T)
# names(resultJson)
# str(resultJson)
sdgtest <- resultJson$value 

sdgtest_ <- sdgtest %>% 
  select(- c("_RecordID", "Sys_RowTitle", "Sys_Version", "Sys_VersionID", "Sys_OriginCode", "Sys_LoadBy", "Sys_CommitDateUtc", 
             "Sys_FirstLoadBy", "Sys_FirstCommitDateUtc", "Sys_ID", "Sys_BatchID", "Sys_FirstBatchID", "Sys_PK", "OBSERVATION_STATUS")) %>% 
  filter(DIM_TIME_TYPE != "YEAR_RANGE") %>% 
  mutate(DIM_TIME = as.numeric(DIM_TIME)) %>% 
  filter(DIM_TIME>=2000) %>% 
  left_join(ind_func %>% select(-c(Language)) %>% rename(IND_CODE = IndicatorCode)) %>% 
  arrange(IndicatorName, DIM_TIME)

# Global Data
response <- GET("https://xmart-api-public.who.int/DATA_/RELAY_MAY2023?$filter=DIM_GEO_CODE_M49%20eq%20'001'")
resultTxt <- content(response, "text")
resultJson <- fromJSON(resultTxt, flatten = T)
# names(resultJson)
# str(resultJson)
sdgtest_glob <- resultJson$value

sdgtest_glob_ <- sdgtest_glob %>% 
  select(- c("_RecordID", "Sys_RowTitle", "Sys_Version", "Sys_VersionID", "Sys_OriginCode", "Sys_LoadBy", "Sys_CommitDateUtc", 
             "Sys_FirstLoadBy", "Sys_FirstCommitDateUtc", "Sys_ID", "Sys_BatchID", "Sys_FirstBatchID", "Sys_PK", "OBSERVATION_STATUS")) %>% 
  filter(DIM_TIME_TYPE != "YEAR_RANGE") %>% 
  mutate(DIM_TIME = as.numeric(DIM_TIME)) %>% 
  filter(DIM_TIME>=2000) %>% 
  left_join(ind_func %>% select(-c(Language)) %>% rename(IND_CODE = IndicatorCode)) %>% 
  arrange(IndicatorName, DIM_TIME)

sdgtest_all <- rbind(sdgtest_, sdgtest_glob_) %>% 
  mutate(country = case_when(
    DIM_GEO_CODE_M49=="001" ~ "Global",
    DIM_GEO_CODE_M49=="004" ~ "Afghanistan",
  ))

color_line <- c("Global" = "#80BC00",
                "Afghanistan" = "#009ADE")

# ind1 <- sdgtest_ %>% 
ind1 <- sdgtest_all %>% 
  filter(IndicatorName=="New HIV infections (per 1000 uninfected population)") %>% 
  ggplot() +
  labs(title = str_wrap("New HIV infections (per 1000 uninfected population)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
  scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3)
  )

ind2 <- sdgtest_all %>% 
  filter(IndicatorName=="Incidence of tuberculosis (per 100 000 population per year)") %>% 
  ggplot() +
  labs(title = str_wrap("Incidence of tuberculosis (per 100 000 population per year)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
  scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind3 <- sdgtest_all %>% 
  filter(IndicatorName=="Maternal mortality ratio (per 100 000 live births)") %>% 
  ggplot() +
  labs(title = str_wrap("Maternal mortality ratio (per 100 000 live births)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind4 <- sdgtest_all %>% 
  filter(IndicatorName=="Under-five mortality rate (probability of dying by age 5 per 1000 live births)" &
           DIM_MEMBER_1_CODE=="TOTAL") %>% 
  ggplot() +
  labs(title = str_wrap("Under-five mortality rate (probability of dying by age 5 per 1000 live births)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind5 <- sdgtest_all %>% 
  filter(IndicatorName== "Neonatal mortality rate (per 1000 live births)") %>% 
  ggplot() +
  labs(title = str_wrap("Neonatal mortality rate (per 1000 live births)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind6 <- sdgtest_all %>% 
  filter(IndicatorName=="Estimated malaria incidence (per 1000 population at risk)") %>% 
  ggplot() +
  labs(title = str_wrap("Estimated malaria incidence (per 1000 population at risk)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )
  
wrap_plots(ind1, ind2, ind3, ind4, ind5, ind6, ncol = 2) + plot_layout(guides = "collect") & theme(legend.position = "bottom", legend.title = element_blank())

```

\newpage

\Large Health Statistics: Risk Factors
\
\normalsize Indicator Progress
\vspace{-0.5cm} 
```{r risk factors, fig.height=10.3, fig.width = 8, fig.align='center', message=F, warning=F}

ind7 <- sdgtest_all %>% 
  filter(IndicatorName=="Prevalence of hypertension among adults aged 30-79 years, age-standardized" & 
           DIM_MEMBER_1_CODE=="TOTAL") %>% 
  ggplot() +
  labs(title = str_wrap("Prevalence of hypertension among adults aged 30-79 years, age-standardized (%)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
  scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3)
  )

ind8 <- sdgtest_all %>% 
  filter(IndicatorName=="Prevalence of obesity among children and adolescents, BMI > +2 standard deviations above the median (crude estimate) (%)"& 
           DIM_MEMBER_1_CODE=="TOTAL" &
           DIM_MEMBER_2_CODE=="Y5T19") %>% 
  ggplot() +
  labs(title = str_wrap("Prevalence of obesity among children and adolescents (%)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
  scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind9 <- ind9 <- sdgtest_all %>% 
  filter(IndicatorName=="Proportion of population with primary reliance on clean fuels and technologies for cooking (%)" &
           DIM_MEMBER_1_CODE=="TOTAL") %>% 
  ggplot() +
  labs(title = str_wrap("Proportion of population with primary reliance on clean fuels and technologies (%)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind10 <- sdgtest_all %>% 
  filter(IndicatorName=="Concentrations of fine particulate matter (PM2.5)" &
           DIM_MEMBER_1_CODE=="TOTAL") %>% 
  ggplot() +
  labs(title = str_wrap("Concentrations of fine particulate matter (PM2.5)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind11 <- sdgtest_all %>% 
  filter(IndicatorName== "Alcohol, total per capita (15+) consumption (in litres of pure alcohol) (SDG Indicator 3.5.2), three-year average"&
           DIM_MEMBER_1_CODE=="TOTAL") %>% 
  ggplot() +
  labs(title = str_wrap("Total alcohol per capita (>= 15 years of age) consumption (litres of pure alcohol)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )

ind12 <- sdgtest_all %>% 
  filter(IndicatorName=="Population with basic handwashing facilities at home (%)"&
           DIM_MEMBER_1_CODE=="TOTAL") %>% 
  ggplot() +
  labs(title = str_wrap("Proportion of population using a hand-washing facility with soap and water (%)", 45))+
  geom_line(aes(x=DIM_TIME, y = VALUE_NUMERIC, color = country), size = 1)+
    scale_color_manual(values = color_line)+
  theme_classic()+
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
  )
  
wrap_plots(ind7, ind8, ind9, ind10, ind11, ind12, ncol = 2) + plot_layout(guides = "collect") & theme(legend.position = "bottom", legend.title = element_blank())

```

\newpage
\vspace{-0.3cm} 
\Large WHO Triple Billion progress
\
\
\normalsize Number of people affected (millions)
```{r tripbil, fig.height=3.5, fig.width = 8, fig.align='center'}
# names(resultJson)
# str(resultJson)
# all_datasets <- resultJson$value
response <- GET("https://xmart-api-public.who.int/DATA_/RELAY_3B")
response <- GET("https://xmart-api-public.who.int/DATA_/RELAY_3B_DATA?$filter=DIM_GEO_CODE_M49%20eq%20'004'")

resultTxt <- content(response, "text")
resultJson <- fromJSON(resultTxt, flatten = T)
tripb <- resultJson$value 

tripb_ <- tripb %>% 
  group_by(DIM_GEO_CODE_M49, TRIPLE_BILLION, DIM_TIME) %>% 
  summarise(contrib = sum(COUNT_N)) %>% 
  ungroup() %>% 
  mutate(year = as.numeric(DIM_TIME)) %>% 
  mutate(tb = case_when(
    TRIPLE_BILLION=="HPOP" ~ "Healthier Populations",
    TRIPLE_BILLION=="HEP" ~ "Health Emergencies Protection",
    TRIPLE_BILLION=="UHC" ~ "Universal Health Coverage"
  )) %>% 
  mutate(contrib_m = round(contrib/1000000, 1))
  
tripb_  %>% 
  filter(year<=2025) %>% 
  ggplot() +
  geom_line(aes(x=year, y = contrib_m, color = tb), show.legend = F, size = 1)+
  geom_text(data = tripb_ %>% filter(year==2025),
            aes(x = 2026, y = contrib_m, label = paste0(contrib_m, "m \n(", tb, ")"), color = tb), show.legend = F, size = 3) +
  scale_x_continuous(breaks = c(2018,2019, 2020, 2021, 2022, 2023, 2024, 2025), limits = c(2018, 2027)) +
  scale_color_manual(values = c("Healthier Populations" = "#5B2C86",
                                "Health Emergencies Protection" = "#A6228C",
                                "Universal Health Coverage" = "#80BC00"))+
  theme_classic() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_blank(),
    axis.line.x = element_line(color = "darkgrey",linetype = 3),
    panel.grid.major = element_line(color = "darkgrey",size = 0.5,linetype = 3),
    legend.title = element_blank(),
    legend.position = "top"
  )
```
\small 
In Afghanistan, by 2025 the number of additional people projected to be: enjoying better health and wellbeing is 10.6 million; covered by essential services and not experiencing financial hardship is 1.2 million; and protected from health emergencies is 13.2 million.
\
\
\
\normalsize Healthier Populations - individual indicator contributions (millions)
```{r hpopcontrib, fig.align='center', fig.width = 8, fig.height=4}
all_plt_dat <- arrow::read_parquet("C:\\Users\\samra\\Documents\\WHS_app\\input\\2024-03-26-10-06_summary.parquet") %>%
  mutate(country = whoville::iso3_to_names(aggregate_id),
         country = ifelse(is.na(country),
                          case_when(
                            aggregate_id=="global" ~"Global",
                            aggregate_id=="AFR" ~"African Region",
                            aggregate_id=="AMR" ~"Region of the Americas",
                            aggregate_id=="EMR" ~"Eastern Mediterranean Region",
                            aggregate_id=="EUR" ~"European Region",
                            aggregate_id=="SEAR" ~"South-East Asia Region",
                            aggregate_id=="WPR" ~"Western Pacific Region"
                          ),
                          country)
  ) %>%
  mutate(
    contribution = mean_contribution,
    contribution_mln = contribution / 1e6
  )
config_all <- config::get(
  file = "C:\\Users\\samra\\Documents\\WHS_app\\input\\all.yml",
  config = Sys.getenv("USER")
)

ind_labels <- openxlsx::readWorkbook("C:\\Users\\samra\\Documents\\WHS_app\\input\\indicator_labels WHS 2.xlsx")

get_inds <- function(get_forecast_inds = TRUE, get_billion_inds = FALSE) {
  stopifnot(
    "Exactly one of 'get_forecast_inds' and 'get_billion_inds' can be TRUE" =
      xor(get_forecast_inds, get_billion_inds)
  )
  
  if (get_forecast_inds) {
    inds_possible <- list(
      uhc = billionaiRe::billion_ind_codes("uhc") %>%
        purrr::discard(~.x %in% c("hwf", "fh")),
      hpop = billionaiRe::billion_ind_codes("hpop"),
      hep = billionaiRe::billion_ind_codes("hep", include_subindicators = FALSE) %>%
        purrr::discard(~stringr::str_ends(.x, "_campaign")) %>%
        # don't need since we estimate 'detect_respond' directly
        purrr::discard(~.x %in% c("detect", "respond", "notify")) %>%
        purrr::discard(~.x %in% c("surviving_infants"))
    )
  }
  else if (get_billion_inds) {
    inds_possible <- list(
      uhc = billionaiRe::billion_ind_codes("uhc") %>%
        purrr::discard(~.x %in% c("doctors", "nurses")),
      hpop = billionaiRe::billion_ind_codes("hpop"),
      hep = billionaiRe::billion_ind_codes("hep", include_subindicators = FALSE) %>%
        # don't need since we estimate 'detect_respond' directly
        purrr::discard(~.x %in% c("detect", "respond", "notify")) %>%
        purrr::discard(~.x %in% c("surviving_infants"))
    )
  }
  
  return(inds_possible)
}
inds <- get_inds(get_forecast_inds = FALSE, get_billion_inds = TRUE)
inds$uhc <- c(inds$uhc, "population")
inds$hep <- config_all$hep_intermediate_inds
inds_summary <- c("hpop" = "hpop_healthier", "uhc" = "uhc_billion", "hep" = "hep_idx")

inds_all <- inds %>%
  unlist(use.names = FALSE) %>%
  unique() %>%
  c(inds_summary) %>%
  unname()

# country = "Thailand"; country_iso = "THA"

`%!in%` = Negate(`%in%`)

country_ <- "Afghanistan"

all_plt_dat <- all_plt_dat %>% 
      filter(
        country == country_,
        scenario == "baseline",
        ind %in% inds_all,
        year >= config_all$required_start_year,
        year <= 2025,
        year > 2017
      ) %>%
      left_join(ind_labels, by = c("ind", "billion")) %>%
      mutate(name = case_when(name == "Child healthcare" ~ "Child health care", .default = name))

hpop_ind_order <- all_plt_dat %>%
  filter(year == 2025 & billion == "hpop" & ind != "hpop_healthier") %>%
  arrange(abs(contribution)) %>%
  pull(name)

# hpop_ind_colors <- full_color_pal[1:length(hpop_ind_order)]
# names(hpop_ind_colors) <- hpop_ind_order
      
hpop_decomp <- all_plt_dat %>%
  mutate(ind = factor(name, levels = c(hpop_ind_order, "Population healthier - HPOP Billion"))) %>%
  filter(billion == "hpop") 

plt_billion = "hpop"
plt_net_ind = "Population healthier - HPOP Billion"
# plt_inds_color_pal = hpop_ind_colors
label_years = config_all$years_label_plot %>% c(2019)
size_text = 3
plt_dat = hpop_decomp
  
net_dat <- plt_dat %>%
  filter(ind == plt_net_ind) %>%
  mutate(
    point_label = case_when(
      year %in% label_years ~ contribution_mln %>% round(digits = 0),
      .default = NA_real_
      )
  ) %>%
  select(ind, year, contribution_mln, point_label)
  
calc_label_points <- function(dat) {
    dat %>%
      mutate(
        ind_idx = as.integer(ind),
        ind_label = ind
      ) %>%
      arrange(-ind_idx) %>%
      mutate(
        y_upper_bar = cumsum(contribution_mln),
        y_lower_bar = c(0, y_upper_bar[-n()]),
        y_midpoint = (y_upper_bar + y_lower_bar) / 2,
      ) %>%
      select(ind, ind_idx, ind_label, year, contribution_mln, y_upper_bar, y_lower_bar, y_midpoint)
  }
  
  label_positive_points <- plt_dat %>%
    filter(year == 2025 & contribution_mln >= 0 & ind != plt_net_ind) %>%
    calc_label_points()
  label_negative_points <- plt_dat %>%
    filter(year == 2025 & contribution_mln < 0 & ind != plt_net_ind) %>%
    calc_label_points()
  label_points <- bind_rows(label_positive_points, label_negative_points) %>%
    mutate(
      pct_contribution = abs(contribution_mln) / sum(abs(contribution_mln)) * 100,
      ind_label = case_when(
        plt_billion == "hep" ~ ind,
        pct_contribution > 1 ~ ind,
        .default = NA
      )
    )
  label_ind_in_legend <- label_points %>%
    filter(is.na(ind_label)) %>%
    arrange(ind) %>%
    pull(ind)
  
  plt_dat <- plt_dat %>%
    filter(ind != plt_net_ind) %>%
    mutate(ind_label = if_else(year == 2025, ind, NA)) %>%
    select(ind, year, ind_label, contribution_mln)
  
target_color <- "#F26829" 
below <- label_points %>% 
  filter(contribution_mln < 0) %>% 
  arrange(contribution_mln) %>% 
  distinct(ind) %>% pull()
num_colors <- length(below)
# Number of colors in the gradient
color_gradient <- colorRampPalette(c("#feece0", target_color))(num_colors)
names(color_gradient) <- below

target_color <- "#009ADE"
above <- label_points %>% 
  filter(contribution_mln > 0) %>% 
  arrange(desc(contribution_mln)) %>% 
  distinct(ind) %>% pull()
num_colors <- length(above)
# Number of colors in the gradient
color_gradient2 <- colorRampPalette(c("#ddeff9", target_color))(num_colors)
names(color_gradient2) <- above

color_final <- c(color_gradient2, color_gradient)
ind_sent <- paste(label_ind_in_legend, collapse = ', ')
nudgeing <- net_dat %>% filter(year==2019) %>% pull(contribution_mln)

plt_dat %>%
  # filter(year<=2025) %>% 
    ggplot(aes(x = year, y = contribution_mln)) +
    geom_col(aes(fill = ind), position = "stack", na.rm = F, show.legend = F) +
    geom_line(data = net_dat, aes(y = contribution_mln, color = "Net Contribution"),  color = "black") +
    geom_point(data = net_dat, aes(y = contribution_mln, color = "Net Contribution"), color = "black") +
    geom_text_repel(
      data = label_points,
      mapping = aes(x = 2025.45, y = y_midpoint, label = ind_label), #, color = ind
      color = "black",
      # vjust aligns the segments vertically in the middle of each bar section
      # position = position_stack(vjust = 0.5),
      na.rm = T,
      # align all indicator labels at 20301 onwards and only shift vertically
      direction = "y",
      # nudge_y = 1,
      xlim = c(2026, Inf),
      # still label indicators that are close to equal
      max.overlaps = 100,
      # effectively skip drawing line to label
      # min.segment.length = 100,
      show.legend = FALSE,
      size = size_text
    ) +
  geom_text_repel(
    data = net_dat %>% filter(year==2019),
      aes(x = year, y = contribution_mln, label = "Net contribution"),
      show.legend = F, na.rm = T, size = 3, color = "black",
      nudge_y = nudgeing
    ) +
    geom_hline(yintercept = 0, linetype = "solid", alpha = 0.5) +
    scale_fill_manual(
      values = color_final,
      breaks = label_ind_in_legend
    ) +
    scale_x_continuous(breaks = 2018:2025) +
    scale_y_continuous(n.breaks = 10) +
    theme_classic() +
    # Allow labels to bleed past the canvas boundaries
    coord_cartesian(clip = 'off') +
    theme(
      panel.grid.major.y = element_line(color = "darkgrey"),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.line.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.x=element_text(size=8),
      axis.title.x =element_blank(),
      axis.text.y=element_text(size=8),
      axis.title.y=element_blank(),
      plot.title = element_blank(),
      plot.margin = unit(c(5, 100, 5, 5), "pt"),
    )
```
\small Other indicators below 1% of the total absolute contribution in 2025: `r ind_sent`.
